### 2016-11-23 Detector/Detector.tex
More HCAL stuff

The \ac{HB} is a sampling calorimeter made of brass absorber
plates with

\subsection{Muon system}
\label{sec:CMSLHC_CMS_muons}

>>>>

The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
plates with tiles of plastic scintillator as the active material. The tiles 
are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
beyond this range.
The light from each tile is collected with a wavelength-shifting fibre, 
which is eventually read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
sufficient to identify for example late-starting showers. The \ac{HO}, sitting
outside of the magnet and using the coil as an additional absorber, extends the 
thickness to at least 11.8 interaction lenghts. 
The active material again consists of plastic scintillator tiles which roughly
map the granularity of the tiles in the \ac{HB}, read out by feeding the light
to a hybrid photodiode via wavelength shifting fibres.
%WTF: wavelength-shifting fibres

The \ac{HF}, providing coverage in the very forward region, is 
subjected to large radiation doses, requiring an extremely
radiation hard active material. For this reason quartz
fibres are used as active material. These fibres are embedded
in the steel absorber structure. Charged particles from the
shower initiated in the steel generate Cherenkov light in 
the quartz fibres, which is read out by photomultiplier tubes.
%Half of the fibres run over the full depth of the absorber
%while the other half starts at a depth of 22 cm, this is
%to distinguish electrons and photons (which deposit a large
%fraction of their energy in the first 22cm) from hadrons.

HCAL RESOLUTION!

\subsection{Muon system}
\label{sec:CMSLHC_CMS_muons}
One of the main physics goals of the \ac{CMS} experiment
at design was to search for $H\rightarrow ZZ\rightarrow 4\mu$ decays. Muons
suffer less from radiative losses in the tracker material, which means the most accurate
4-body mass can be constructed when searching for muon final states.
After discovery of the Higgs boson, the ZZ channel remains important
for Higgs measurements, while many \ac{BSM} searches make use 
they
